### 2025-06-15 manuscripts/10-JERP-v3/manuscript_main.tex
some edits to ref response

Let $Y_{ist}$ be the outcome of interest for person $i$ in state $s$ at time $t$. $HW_{ist}$ is an indicator variable equal to one if person $i$ has a Hispanic father and US-born mother, and zero if person $i$ has a US-born father and Hispanic mother. $X_{ist}$ is a vector of controls that includes age, hours worked, and synthetic parents' characteristics (income and education), $\gamma_{st}$ represents state-year fixed effects, and $\phi_{ist}$ is the error term. The equation for this strategy is written as follows, and the sample is restricted to individuals from WH and HW families:

@@

It is important to address potential statistical inference issues related to using synthetic parents' characteristics as control variables. The parental characteristics are included solely as controls and not for inference purposes. I do not interpret these coefficients, as my primary interest lies in $\beta_1$, which captures the gap between Hispanic and White last names. Since I am using these synthetic characteristics purely as controls, without drawing any conclusions from their coefficients, this should not affect the standard errors or p-values of my coefficient of interest $\beta_1$.

The synthetic parents are constructed using the birth year of the child and are not based on actual parents in the CPS sample at the time of the survey. The place of birth of parents—mothers and fathers—are questions asked of all participants in the Current Population Survey (CPS) starting 1994. Therefore, I do not use the information of parents who are in the CPS sample at the time of the survey, but rather construct synthetic parents from Census data. This approach means that concerns about non-random attrition of parents from the CPS sample do not apply to my analysis.

@@

I present the results from estimating equation \ref{eq:1a} in Table \ref{tab:lastname-ed-reg}. I estimate the mean educational outcomes of White Hispanic, US-born individuals ages 25-40. I also restrict the sample to children of HW and WH parents, and the omitted group is children of WH parents. Column 1 in Table \ref{tab:lastname-ed-reg} is the difference in total years of education between HW children and their WH peers. Column 2 is the difference in the probability of dropping out of high school. Column 3 is the difference in the probability of having an associate degree. Column 4 is the difference in the probability of having a bachelor’s degree. All regressions include controls for age, parental education and income, and state-year fixed effects.

There is a significant gap in total years of education between HW and WH children. HW children receive 0.2 fewer years of education than WH children. The gap between HW and WH women is larger than the gap between HW and WH men. Women with a Hispanic last name receive 0.25 fewer years of education than WH women. The gap between HW and WH men is 0.16 years.

Although there is a modest yet statistically significant gap in total years of education between HW and WH children, there is no significant difference in the probability of dropping out of high school. The gap between HW and WH high school dropouts is statistically insignificant (1 percentage point). The same is true for HW women (2 percentage points) and men (0 percentage points).

Notable differences emerge for higher education outcomes. HW children are 2 percentage points less likely to earn an associate degree compared to their WH peers, representing a 13.3\% reduction relative to the WH associate degree rate of 15\%. Similarly, they are 3 percentage points less likely to earn a bachelor's degree, a 13\% reduction compared to the WH bachelor's degree rate of 23\%. These differences are slightly larger for HW women, who are 3 percentage points less likely to earn an associate degree and 4 percentage points less likely to earn a bachelor’s degree. For HW men, the gap is 2 percentage points for an associate degree and statistically insignificant for a bachelor’s degree.

These results suggest that while the overall educational gap between HW and WH children is small in terms of years of education, the disparities become more pronounced when considering higher education milestones, particularly for HW women. Given HW mothers are more educated, HW children's lower degree attainment may reflect structural barriers in higher education access---such as lower counselor encouragement, less access to AP courses, or name-based scholarship bias.

@@

I provide the results of the estimating equation \ref{eq:1a} in Tables \ref{tab:lastnamereg-emp} and \ref{tab:lastnamereg} on unemployment and log earnings. I estimate the mean unemployment and mean wages of White US-born Hispanic men aged 25-40 who are employed full-time. I also restrict the sample to children of HW and WH (omitted) parents.  Column 1 in Table \ref{tab:lastnamereg} is the average crude earnings gap in log annual earnings between HW workers and their WH peers. In the next 4 columns, I introduce the results with controls for hours worked, state fixed effects (FE), year FE, age FE, education FE, and parental background.

I also analyzed the effect of likely having a Hispanic last name on unemployment rates. Table \ref{tab:lastnamereg-emp} presents the results of this analysis. Column 1 shows that individuals who likely have Hispanic last names (HW) have a 1 percentage point higher unemployment rate compared to those with White last names. This discrepancy persists even after controlling for age, state FE, year FE, and state-year FE (Column 2), though the significance is lower. When education is included as a control (Column 3), the gap remains at 1 percentage point. Finally, after controlling for parental background (Column 4), the 1 percentage point difference in unemployment rates becomes statistically insignificant. These results suggest that while there is an initial unemployment gap associated with likely having a Hispanic last name, much of this difference can be explained by factors such as education and parental background and does not necessarily reflect discrimination. The mean unemployment rate for individuals with Hispanic last names (HW) is 7\% across all specifications.

@@

This study uses surname-based ethnic cues to show that individuals with Hispanic-sounding names face educational and earnings disadvantages, even when born into similarly situated interethnic families. By comparing children of interethnic marriages, I find that individuals who likely have Hispanic-sounding last names receive 0.2 fewer years of education than their counterparts who likely have White-sounding last names, representing a 1.4\% reduction. This gap is larger for women (0.25 years, or 1.8\%) than for men (0.16 years, or 1.2\%). In labor market outcomes, those with likely Hispanic surnames are 1 percentage point more likely to be unemployed (a 14.3\% increase from the mean rate) and earn 5 percentage points (4.9\%) less than their counterparts.

While the overall impact on total years of education appears modest, the disparities become more pronounced in higher education attainment—with a 13.3\% reduction in associate degree completion and 13\% reduction in bachelor's degree attainment. These patterns are especially pronounced for women with Hispanic surnames, who face larger discrepancies in both total education and degree completion (14.8\% reduction in bachelor's degree attainment). This study highlights how surname---especially in interethnic families---can serve as subtle but powerful signals of ethnic identity that continue to shape educational attainment and labor market inequality in the United States.

>>>>

Let $Y_{ist}$ be the outcome of interest for person $i$ in state $s$ at time $t$. $HW_{ist}$ is an indicator variable equal to one if person $i$ has a Hispanic father and US-born mother, and zero if person $i$ has a US-born father and Hispanic mother. $X_{ist}$ is a vector of controls that includes age, and hours worked, $\gamma_{st}$ represents state-year fixed effects, and $\phi_{ist}$ is the error term. The equation for this strategy is written as follows, and the sample is restricted to individuals from WH and HW families:

@@

@@

I present the results from estimating equation \ref{eq:1a} in Table \ref{tab:lastname-ed-reg}. I estimate the mean educational outcomes of White Hispanic, US-born individuals ages 25-40. I also restrict the sample to children of HW and WH parents, and the omitted group is children of WH parents. Column 1 in Table \ref{tab:lastname-ed-reg} is the difference in total years of education between HW children and their WH peers. Column 2 is the difference in the probability of dropping out of high school. Column 3 is the difference in the probability of having an associate degree. Column 4 is the difference in the probability of having a bachelor’s degree. All regressions include controls for age and state-year fixed effects.

There is a significant gap in total years of education between HW and WH children. HW children receive 0.39 fewer years of education than WH children. The gap between HW and WH women is larger than the gap between HW and WH men. Women with a Hispanic last name receive 0.42 fewer years of education than WH women. The gap between HW and WH men is 0.38 years.

Although there is a modest yet statistically significant gap in total years of education between HW and WH children, there is no significant difference in the probability of dropping out of high school. The gap between HW and WH high school dropouts is statistically insignificant (1 percentage point). The gap between HW and WH women is statistically significant and equal to 2 percentage points, while the gap between HW and WH men is statistically insignificant.

Notable differences emerge for higher education outcomes. HW children are 3 percentage points less likely to earn an associate degree compared to their WH peers, representing a 20\% reduction relative to the WH associate degree rate of 15\%. Similarly, they are 6 percentage points less likely to earn a bachelor's degree, a 22.2\% reduction. These differences are slightly larger for HW women, who are 4 percentage points less likely to earn an associate degree and 7 percentage points less likely to earn a bachelor’s degree. For HW men, the gap is 3 percentage points for an associate degree and 6 percentage points for a bachelor’s degree.

These results suggest that while the overall educational gap between HW and WH children is small in terms of years of education, the disparities become more pronounced when considering higher education milestones, particularly for HW women. Given HW mothers are, on average, more educated, HW children's lower degree attainment may reflect structural barriers in higher education access---such as lower counselor encouragement, less access to AP courses, or name-based scholarship bias.

@@

I provide the results of the estimating equation \ref{eq:1a} in Tables \ref{tab:lastnamereg-emp} and \ref{tab:lastnamereg} on unemployment and log earnings. I estimate the mean unemployment and mean wages of White US-born Hispanic men aged 25-40 who are employed full-time. I also restrict the sample to children of HW and WH (omitted) parents.  Column 1 in Table \ref{tab:lastnamereg} is the average crude earnings gap in log annual earnings between HW workers and their WH peers. In the next 4 columns, I introduce the results with controls for hours worked, state fixed effects (FE), year FE, age FE, and education FE.

I also analyzed the effect of likely having a Hispanic last name on unemployment rates. Table \ref{tab:lastnamereg-emp} presents the results of this analysis. Column 1 shows that individuals who likely have Hispanic last names (HW) have a 1 percentage point higher unemployment rate compared to those with White last names. This discrepancy persists even after controlling for age, state FE, year FE, and state-year FE (Column 2), though the significance is lower. When education is included as a control (Column 3), the gap remains at 1 percentage point. These results suggest that while there is an initial unemployment gap associated with likely having a Hispanic last name, much of this difference can be explained by factors such as educational background and does not necessarily reflect discrimination. The mean unemployment rate for individuals with Hispanic last names (HW) is 7\% across all specifications.

@@

This study uses surname-based ethnic cues to show that individuals with Hispanic-sounding names face educational and earnings disadvantages, even when born into similarly situated interethnic families. By comparing children of interethnic marriages, I find that individuals who likely have Hispanic-sounding last names receive 0.39 fewer years of education than their counterparts who likely have White-sounding last names, representing a 2.9\% reduction. This gap is larger for women (0.42 years, or 2.9\%) than for men (0.38 years, or 2.8\%). In labor market outcomes, those with likely Hispanic surnames are 1 percentage point more likely to be unemployed (a 14.3\% increase from the mean rate) and earn 5 percentage points (4.9\%) less than their counterparts.

While the overall impact on total years of education appears modest, the disparities become more pronounced in higher education attainment—with a 15\% reduction in associate degree completion and 22.2\% reduction in bachelor's degree attainment. These patterns are especially pronounced for women with Hispanic surnames, who face larger discrepancies in both total education and degree completion (14.8\% reduction in bachelor's degree attainment). This study highlights how surname---especially in interethnic families---can serve as subtle but powerful signals of ethnic identity that continue to shape educational attainment and labor market inequality in the United States.

### 2025-06-15 manuscripts/10-JERP-v3/submit_journal-main.tex
Updates from Overleaf
some edits to ref response

\begin{spacing}{\rrxspc}
    I am grateful to the referee for raising this important concern. I have expanded the discussion of these methodological issues in the empirical approach section. Regarding the generated regressor issue: ``The parental characteristics are included solely as controls and not for inference purposes. I do not interpret these coefficients, as my primary interest lies in $\beta_1$, which captures the gap between Hispanic and White last names. Since I am only using these synthetic characteristics as controls and not making inference about their coefficients, this should not affect the standard errors or p-values of my coefficient of interest $\beta_1$.''

    Regarding the clustering concern: To address this issue, I re-estimated the log annual earnings model using standard errors clustered at the parental birthplace level (mother's and father's birthplace), which corresponds to the level at which `synthetic' parental characteristics were estimated---see table below. The clustered standard errors for $\beta_1$ became slightly smaller (ranging from 0.00 to 0.01 across specifications) compared to the original specification. The fact that standard errors decreased rather than increased after clustering indicates that the original standard errors were, if anything, conservative for my main coefficient of interest. Moreover, since immigrants from Spanish-speaking countries have strong heterogeneous geographical preferences on where to live, clustering at the state level would further address the concern raised by the referee. For example, Cuban immigrants strongly select Florida when they move to the US, while Mexican immigrants self-select to California and Texas. This geographical clustering pattern actually strengthens the case for state-level clustering, as it directly addresses the referee's concern about spatial correlation in the error term. By clustering standard errors at the state level, I account for this within-state correlation that arises from the non-random geographical distribution of immigrant groups.

@@

\newgeometry{bottom=1.0in}
\input{10-JERP-v3/tab0000-regression-cluster}
\restoregeometry

\begin{spacing}{\rrxspc}
\begin{quotation}
    \textbf{R1: } 5. The paper would be improved through an expanded discussion of the impact of measurement error on the reported estimates. While there is a well understood result in the measurement error literature that measures of group mean parental education will provide estimates that are more robust to the presence of measurement error in individual level measures of parental education, there is still an issue with the non-random attrition of potential parents. Specifically, not all potential parents have children in the CPS sample, nor do all children in the CPS sample have parents in the sample of potential parents. Moreover, the non-random attrition of potential parents implies that mean parental education may be systematically higher or lower than the actual parental education of the children in the CPS sample. The paper would be improved by providing an expanded discussion of the likely impacts of measurement error on the reported estimates.
    \end{quotation}
\end{spacing}
\begin{spacing}{\rrxspc}
    Thank you for your comments. I have clarified this methodological point and expanded the discussion of measurement error concerns. First, I want to clarify that the concern about attrition does not apply to my analysis: The synthetic parents are constructed using the birth year of the child and are not based on actual parents in the CPS sample at the time of the survey. The place of birth of parents---mothers and fathers---are questions asked of all participants in the Current Population Survey (CPS) starting 1994. Therefore, I do not use the information of parents who are in the CPS sample at the time of the survey, and I construct synthetic parents from Census data. Because this approach uses Census data rather than contemporaneous parent-child pairs, concerns about non-random attrition of parents from the CPS sample do not apply to my analysis. 
    \end{spacing}

\begin{spacing}{\rrxspc}     
    Regarding measurement error more broadly, I have expanded the discussion in the empirical approach section: ``A potential concern is measurement error in using CPS data to infer parental ethnicity, since it relies on place of birth rather than self-identified Hispanic origin. However, during the period studied, second-generation Hispanics were rare: only about 3\% of native-born Americans identified as Hispanic (see Table \ref{tab:mat3}, which presents Hispanic identification rates by nativity). This makes it unlikely that US-born parents in interethnic unions are second-generation+ Hispanic immigrants.''
    \end{spacing}
\begin{spacing}{\rrxspc}
    Additionally, while using census averages for synthetic parent characteristics does introduce some imprecision compared to actual parent data, this approach avoids the selection bias that would arise from using only parent-child pairs who remain in the CPS sample. The synthetic parents methodology, used by \textcite{rubinstein2014pride}, provides population-level averages that are more representative than the selected sample of parents who happen to be surveyed alongside their children. Moreover, since these synthetic parent controls are not interpreted causally, any measurement error from using group means rather than individual-level data is unlikely to bias the estimated surname effect, which is the key parameter of interest.
    \end{spacing}

>>>>

\begin{spacing}{\rrxspc}
    I am grateful to the referee for raising this important concern. I have expanded the discussion of these methodological issues in the empirical approach section. Regarding the generated regressor issue, I updated the regression results in the manuscript with results that do not include the specification where  `synthetic parents` are included in the controls. This alleviates the concern regarding generated, as they are no longer in the regression.

@@

\begin{spacing}{\rrxspc}
\begin{quotation}
    \textbf{R1: } 5. The paper would be improved through an expanded discussion of the impact of measurement error on the reported estimates. While there is a well understood result in the measurement error literature that measures of group mean parental education will provide estimates that are more robust to the presence of measurement error in individual level measures of parental education, there is still an issue with the non-random attrition of potential parents. Specifically, not all potential parents have children in the CPS sample, nor do all children in the CPS sample have parents in the sample of potential parents. Moreover, the non-random attrition of potential parents implies that mean parental education may be systematically higher or lower than the actual parental education of the children in the CPS sample. The paper would be improved by providing an expanded discussion of the likely impacts of measurement error on the reported estimates.
    \end{quotation}
\end{spacing}
\begin{spacing}{\rrxspc}
    Thank you for your comments. I have clarified this methodological point and expanded the discussion of measurement error concerns. First, I want to clarify that the concern about attrition does not apply to my analysis: Synthetic parents are constructed using the birth year of the child and are not based on actual parents in the CPS sample at the time of the survey. The place of birth of parents---mothers and fathers---are questions asked of all participants in the Current Population Survey (CPS) starting 1994. Therefore, I do not use the information of parents who are in the CPS sample at the time of the survey, and I construct synthetic parents from Census data. Because this approach uses Census data rather than contemporaneous parent-child pairs, concerns about non-random attrition of parents from the CPS sample do not apply to my analysis. 
    \end{spacing}

\begin{spacing}{\rrxspc}     
    Regarding measurement error more broadly, I have expanded the discussion in the empirical approach section to include the following: ``A potential concern is measurement error in using CPS data to infer parental ethnicity, since it relies on place of birth rather than self-identified Hispanic origin. However, during the period studied, second-generation Hispanics were rare: only about 3\% of native-born Americans identified as Hispanic (see Table \ref{tab:mat3}, which presents Hispanic identification rates by nativity). This makes it unlikely that US-born parents in interethnic unions are second-generation+ Hispanic immigrants.''
    \end{spacing}

### 2025-06-15 manuscripts/10-JERP-v3/tab09-regression-weekearn-nonmex.tex
some edits to ref response

\begin{table}[H]
\centering\centering
\caption{Effect of Having Hispanic Last Name: Hispanics with Non-Mexican Ancestry  \label{tab:lastnamereg-weekearm-nonmex}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lccc}
\toprule
  & \specialcell{(1) \\ Log weekly \\ earnings} & \specialcell{(2) \\ Log weekly \\ earnings} & \specialcell{(3) \\  Log weekly \\ earnings}\\
\midrule
$HW_{ist}$ & \num{-0.05}* & \num{-0.07}*** & \num{-0.04}**\\
 & (\num{0.03}) & (\num{0.02}) & (\num{0.02})\\
Constant & \num{6.75}*** &  & \\
 & (\num{0.03}) &  & \\
\midrule
\textit{Controlling for:} &  &  & \\
State FE &  & X & X\\
Year FE &  & X & X\\
State-Year FE &  & X & X\\
Age &  & X & X\\
Education &  &  & X\\
Parental Background &  &  & \\
Observations & \num{3225} & \num{3225} & \num{3225}\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] {\setstretch{1.0}\footnotesize{This table includes the estimation results of equation (\ref{eq:1a}) where the dependent variable is log weekly earnings.}}
\item[2] {\setstretch{1.0}\footnotesize{HW is an indicator variable that is equal to 1 if a person is the child of a Hispanic-father and White-mother.}}
\item[3] {\setstretch{1.0}\footnotesize{The sample is restricted to men working full-time and are wage and salary workers.}}
\item[4] {\setstretch{1.0}\footnotesize{Column one has the regression results when controlling for hours worked, age, education, year and state fixed effects. Column two has the results after controlling for education.}}
\item[5] {\setstretch{1.0}\footnotesize{Standard errors are clustered on the state level.}}
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\begin{table}[H]
\centering\centering
\caption{Effect of Having Hispanic Last Name: Hispanics with Non-Mexican Ancestry  \label{tab:lastnamereg-weekearm-nonmex}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lccc}
\toprule
  & \specialcell{(1) \\ Log weekly \\ earnings} & \specialcell{(2) \\ Log weekly \\ earnings} & \specialcell{(3) \\  Log weekly \\ earnings}\\
\midrule
$HW_{ist}$ & \num{-0.05}* & \num{-0.07}*** & \num{-0.04}**\\
 & (\num{0.03}) & (\num{0.02}) & (\num{0.02})\\
Constant & \num{6.75}*** &  & \\
 & (\num{0.03}) &  & \\
\midrule
\textit{Controlling for:} &  &  & \\
State FE &  & X & X\\
Year FE &  & X & X\\
State-Year FE &  & X & X\\
Age &  & X & X\\
Education &  &  & X\\
Observations & \num{3225} & \num{3225} & \num{3225}\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] {\setstretch{1.0}\footnotesize{This table includes the estimation results of equation (\ref{eq:1a}) where the dependent variable is log weekly earnings.}}
\item[2] {\setstretch{1.0}\footnotesize{HW is an indicator variable that is equal to 1 if a person is the child of a Hispanic-father and White-mother.}}
\item[3] {\setstretch{1.0}\footnotesize{The sample is restricted to men working full-time and are wage and salary workers.}}
\item[4] {\setstretch{1.0}\footnotesize{Column one has the regression results when controlling for hours worked, age, education, year and state fixed effects. Column two has the results after controlling for education.}}
\item[5] {\setstretch{1.0}\footnotesize{Standard errors are clustered on the state level.}}
\end{tablenotes}
\end{threeparttable}
\end{table}

### 2025-06-15 manuscripts/10-JERP-v3/tab13-regression.tex
edit manuscript
some edits to ref response

\begin{table}[H]
\centering\centering
\caption{Effect of Having Hispanic Last Name \label{tab:lastname-ed-reg}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
  & \specialcell{(1) \\ Years of \\ Education} & \specialcell{(2) \\ High School \\ Dropout} & \specialcell{(3) \\ Associate Degree} & \specialcell{(4) \\ Bachelor Degree}\\
\midrule
\addlinespace[0.5em]
\multicolumn{5}{l}{\textit{Panel A: Full Sample}}\\
\midrule \hspace{1em}$HW_{ist}$ & -0.20*** & 0.01 & -0.02*** & -0.03***\\
\hspace{1em} & (0.05) & (0.01) & (0.01) & (0.01)\\
\hspace{1em}Observations & 88377 & 90027 & 66927 & 90027\\
\addlinespace[0.5em]
\multicolumn{5}{l}{\textit{Panel B: Women}}\\
\midrule \hspace{1em}$HW_{ist}$ & -0.25*** & 0.02 & -0.03*** & -0.04***\\
\hspace{1em} & (0.06) & (0.01) & (0.01) & (0.01)\\
\hspace{1em}Observations & 46516 & 47302 & 34334 & 47302\\
\addlinespace[0.5em]
\multicolumn{5}{l}{\textit{Panel C: Men}}\\
\midrule \hspace{1em}$HW_{ist}$ & -0.16** & 0.00 & -0.02** & -0.02\\
\hspace{1em} & (0.07) & (0.01) & (0.01) & (0.01)\\
\hspace{1em}Full Sample's Mean & 13.48 & 0.43 & 0.15 & 0.26\\
\hspace{1em}Observations & 41861 & 42725 & 32593 & 42725\\
Women's Mean & 13.58 & 0.44 & 0.16 & 0.27\\
Men's Mean & 13.38 & 0.43 & 0.14 & 0.24\\
p-value test Women - Men & $p=$0.87 & $p=$0.25 & $p=$0.92 & $p=$0.24\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] {\setstretch{1.0}\footnotesize{This table includes the estimation results of equation (\ref{eq:1a}). All regressions include state-year fixed effects.}}
\item[2] {\setstretch{1.0}\footnotesize{HW is an indicator variable that is equal to 1 if a person is the child of a Hispanic-father and White-mother.}}
\item[3] {\setstretch{1.0}\footnotesize{Standard errors are clustered on the state level.}}
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\begin{table}[H]
\centering\centering
\caption{Effect of Having Hispanic Last Name on Educational Outcomes\label{tab:lastname-ed-reg}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
  & \specialcell{(1) \\ Years of \\ Education} & \specialcell{(2) \\ High School \\ Dropout} & \specialcell{(3) \\ Associate Degree} & \specialcell{(4) \\ Bachelor Degree}\\
\midrule
\addlinespace[0.5em]
\multicolumn{5}{l}{\textit{Panel A: Full Sample}}\\
\midrule \hspace{1em}$HW_{ist}$ & -0.39*** & 0.01 & -0.03*** & -0.06***\\
\hspace{1em} & (0.04) & (0.01) & (0.01) & (0.01)\\
\hspace{1em}Observations & 106905 & 108777 & 79157 & 108777\\
\addlinespace[0.5em]
\multicolumn{5}{l}{\textit{Panel B: Women}}\\
\midrule \hspace{1em}$HW_{ist}$ & -0.42*** & 0.02* & -0.04*** & -0.07***\\
\hspace{1em} & (0.05) & (0.01) & (0.01) & (0.01)\\
\hspace{1em}Observations & 56115 & 57009 & 40322 & 57009\\
\addlinespace[0.5em]
\multicolumn{5}{l}{\textit{Panel C: Men}}\\
\midrule \hspace{1em}$HW_{ist}$ & -0.38*** & 0.01 & -0.03*** & -0.06***\\
\hspace{1em} & (0.06) & (0.01) & (0.01) & (0.01)\\
\hspace{1em}Observations & 50790 & 51768 & 38835 & 51768\\
Full Sample's Mean & 13.57 & 0.42 & 0.15 & 0.27\\
Women's Mean & 13.68 & 0.43 & 0.16 & 0.29\\
Men's Mean & 13.45 & 0.41 & 0.14 & 0.25\\
p-value test Women - Men & $p=$0.48 & $p=$0.12 & $p=$0.46 & $p=$0.41\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] {\setstretch{1.0}\footnotesize{This table includes the estimation results of equation (\ref{eq:1a}). All regressions include state-year fixed effects.}}
\item[2] {\setstretch{1.0}\footnotesize{HW is an indicator variable that is equal to 1 if a person is the child of a Hispanic-father and White-mother.}}
\item[3] {\setstretch{1.0}\footnotesize{Standard errors are clustered on the state level.}}
\end{tablenotes}
\end{threeparttable}
\end{table}

### 2025-06-15 manuscripts/10-JERP-v3/tab16-educ-mex-regression.tex
some edits to ref response

\begin{table}[H]
\centering\centering
\caption{Effect of Having Hispanic Last Name on Educational Outcomes: Hispanics with Mexican Ancestry \label{tab:lastname-ed-reg-mex}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
  & \specialcell{(1) \\ Years of \\ Education} & \specialcell{(2) \\ High School \\ Dropout} & \specialcell{(3) \\ Associate Degree} & \specialcell{(4) \\ Bachelor Degree}\\
\midrule
\addlinespace[0.5em]
\multicolumn{5}{l}{\textit{Panel A: Full Sample}}\\
\midrule \hspace{1em}$HW_{ist}$ & -0.31*** & 0.00 & -0.03*** & -0.04***\\
\hspace{1em} & (0.04) & (0.01) & (0.01) & (0.01)\\
\hspace{1em}Observations & 74926 & 76499 & 61273 & 76499\\
\addlinespace[0.5em]
\multicolumn{5}{l}{\textit{Panel B: Women}}\\
\midrule \hspace{1em}$HW_{ist}$ & -0.35*** & 0.01 & -0.03*** & -0.05***\\
\hspace{1em} & (0.05) & (0.01) & (0.01) & \vphantom{1} (0.01)\\
\hspace{1em}Observations & 39867 & 40608 & 31761 & 40608\\
\addlinespace[0.5em]
\multicolumn{5}{l}{\textit{Panel C: Men}}\\
\midrule \hspace{1em}$HW_{ist}$ & -0.28*** & -0.01 & -0.02*** & -0.04***\\
\hspace{1em} & (0.05) & (0.01) & (0.01) & (0.01)\\
\hspace{1em}Full Sample's Mean & 13.15 & 0.46 & 0.14 & 0.2\\
\hspace{1em}Observations & 35059 & 35891 & 29512 & 35891\\
Women's Mean & 13.26 & 0.46 & 0.15 & 0.22\\
Men's Mean & 13.03 & 0.45 & 0.13 & 0.18\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] {\setstretch{1.0}\footnotesize{This table includes the estimation results of equation (\ref{eq:1a}). All regressions include state-year fixed effects.}}
\item[2] {\setstretch{1.0}\footnotesize{HW is an indicator variable that is equal to 1 if a person is the child of a Hispanic-father and White-mother.}}
\item[3] {\setstretch{1.0}\footnotesize{Standard errors are clustered on the state level.}}
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\begin{table}[H]
\centering\centering
\caption{Effect of Having Hispanic Last Name on Educational Outcomes: Hispanics with Mexican Ancestry \label{tab:lastname-ed-reg-mex}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
  & \specialcell{(1) \\ Years of \\ Education} & \specialcell{(2) \\ High School \\ Dropout} & \specialcell{(3) \\ Associate Degree} & \specialcell{(4) \\ Bachelor Degree}\\
\midrule
\addlinespace[0.5em]
\multicolumn{5}{l}{\textit{Panel A: Full Sample}}\\
\midrule \hspace{1em}$HW_{ist}$ & -0.31*** & 0.00 & -0.03*** & -0.04***\\
\hspace{1em} & (0.04) & (0.01) & (0.01) & (0.01)\\
\hspace{1em}Observations & 74926 & 76499 & 61273 & 76499\\
\addlinespace[0.5em]
\multicolumn{5}{l}{\textit{Panel B: Women}}\\
\midrule \hspace{1em}$HW_{ist}$ & -0.35*** & 0.01 & -0.03*** & -0.05***\\
\hspace{1em} & (0.05) & (0.01) & (0.01) & \vphantom{1} (0.01)\\
\hspace{1em}Observations & 39867 & 40608 & 31761 & 40608\\
\addlinespace[0.5em]
\multicolumn{5}{l}{\textit{Panel C: Men}}\\
\midrule \hspace{1em}$HW_{ist}$ & -0.28*** & -0.01 & -0.02*** & -0.04***\\
\hspace{1em} & (0.05) & (0.01) & (0.01) & (0.01)\\
\hspace{1em}Observations & 35059 & 35891 & 29512 & 35891\\
Full Sample's Mean & 13.15 & 0.46 & 0.14 & 0.2\\
Women's Mean & 13.26 & 0.46 & 0.15 & 0.22\\
Men's Mean & 13.03 & 0.45 & 0.13 & 0.18\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] {\setstretch{1.0}\footnotesize{This table includes the estimation results of equation (\ref{eq:1a}). All regressions include state-year fixed effects.}}
\item[2] {\setstretch{1.0}\footnotesize{HW is an indicator variable that is equal to 1 if a person is the child of a Hispanic-father and White-mother.}}
\item[3] {\setstretch{1.0}\footnotesize{Standard errors are clustered on the state level.}}
\end{tablenotes}
\end{threeparttable}
\end{table}
